Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-03-06 arxiv-submission.tex
Fixed typos

Our findings have profound implications for the nature of turbulence in 
finite temperature superfluids. In circumstances where the vortex density 
$\mathcal{L}$ is large and where the isotropy of the vortex tangle 
is broken by external forcing, the chirality of the flow generated by the 
frequent reconnections may be strong enough to induce an inverse energy 
cascade \cite{notes_recon}.
%The asymmetry of the reconnecting vortex configurations is a key element; 
%when perfectly symmetrical vortex configurations (with corresponding 
%opposite vortex line orientations) reconnect, the injected helicity 
%globally cancels out, as verified in our study if we take also into 
%account the reconnection.
The microscopic mechanism that we have described is probably what
triggers the inverse energy cascade which is observed numerically in  
large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which
indeed inherently not isotropic.
%, hence triggering non-fully reconnections. 
Our work hence motivates further detailed studies of
the role played by helicity in superfluid dynamics 
\cite{dileoni2016,galantucci2021},
moving the emphasis from few vortex systems \cite{scheeler2014} 
to fully coupled superfluid turbulence.

>>>>

Our findings have profound implications for the nature of turbulence in 
finite temperature superfluids. In circumstances where the vortex density 
$\mathcal{L}$ is large and where the isotropy of the vortex tangle 
is broken by external forcing, the chirality of the flow generated by the 
frequent reconnections may be strong enough to induce an inverse energy 
cascade \cite{notes_recon}.
%The asymmetry of the reconnecting vortex configurations is a key element; 
%when perfectly symmetrical vortex configurations (with corresponding 
%opposite vortex line orientations) reconnect, the injected helicity 
%globally cancels out, as verified in our study if we take also into 
%account the reconnection.
The microscopic mechanism that we have described is probably what
triggers the inverse energy cascade which is observed numerically in  
large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is
indeed inherently not isotropic.
%, hence triggering non-fully reconnections. 
Our work hence motivates further detailed studies of
the role played by helicity in superfluid dynamics 
\cite{dileoni2016,galantucci2021},
moving the emphasis from few vortex systems \cite{scheeler2014} 
to fully coupled superfluid turbulence.
